---
title: "toolik_chem"
author: "Joe DeCesaro"
date: "8/11/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
library(janitor)
```

## Part 2
Explore this data package from EDI, which contains a “Data file describing the biogeochemistry of samples collected at various sites near Toolik Lake, North Slope of Alaska”. Familiarize yourself with the metadata (particularly, View full metadata > expand ‘Data entities’ to learn more about the variables in the dataset).

```{r}
toolik_biochem <- read_csv(here::here("data", "2011_Kling_Akchem.csv"), na = ".")

toolik_biochem <- toolik_biochem%>% 
  clean_names()
```

Create a subset of the data that contains only observations from the “Toolik Inlet” site, and that only contains the variables (columns) for pH, dissolved organic carbon (DOC), and total dissolved nitrogen (TDN) (hint: see dplyr::select()). Store this subset as inlet_biochem. Make sure to LOOK AT the subset you’ve created.
```{r}
inlet_biochem <- toolik_biochem %>% 
  filter(site %in% c("Toolik inlet", "Toolik Inlet")) %>% 
  select(p_h, doc_u_m, tdn_u_m)

```

8. Find the mean value of each column three different ways.
```{r}
mean_summary <- inlet_biochem %>% 
  summarize(p_h = mean(p_h, na.rm = TRUE), 
            doc_u_m = mean(doc_u_m, na.rm = TRUE), 
            tdn_u_m = mean(tdn_u_m, na.rm = TRUE))
mean_summary

mean_inlet_biochem <- vector(mode = "numeric", length = ncol(inlet_biochem))

#a
for (i in seq_along(inlet_biochem)) {
  mean_val <- mean(mean_summary[[i]], na.rm = TRUE)
  mean_inlet_biochem[i] <- mean_val
}

mean_inlet_biochem

#b
apply(X = mean_summary, 2, mean, na.rm = TRUE)

#c
map_df(.x = mean_summary, .f = mean)

```




